Data and code for \"Values disclosures and trust in science: A replication study\

### 2022-07-19 readme.Rmd

After cloning and downloading, in Bash or a similar shell run
```
make install
make
```

@@

In R, run
```
renv::restore()
```
to create a local (within-project) package library, with the specific versions used in this project.  Then run the scripts `02_analysis.R` and `03_dag.R`, in that order, to run the analyses.  These scripts will write plots and tables to the `out` folder, creating it if necessary.  Optionally, use `rmarkdown::render()` or the "Knit" button in RStudio to generate HTML documents from these scripts, for comparison with the ones included in the repository.  (Be sure to rename the included HTML files first.)

Finally, in the `paper` folder, from Bash or a similar shell run
```
quarto render paper.Qmd --to pdf
```
to generate the PDF version of the manuscript.

>>>>

After cloning and downloading, in bash or a similar shell run
```
make install
make
```

The installation step primarily installs R packages.  This can take a long time if many packages need to be downloaded.

@@

In R, run
```
renv::restore()
```
to create a local (within-project) package library, with the specific versions used in this project.  Then run the scripts `02_analysis.R` and `03_dag.R`, in that order, to run the analyses.  These scripts will write plots and tables to the `out` folder, creating it if necessary.

Optionally, use `rmarkdown::render()` or the "Knit" button in RStudio to generate HTML documents from these scripts, for comparison with the ones included in the repository.  (Be sure to rename the included HTML files first.)

Finally, in the `paper` folder, from bash or a similar shell run
```
quarto render paper.Qmd --to pdf
```
to generate the PDF version of the manuscript.
